---
title: "R Notebook"
output: html_notebook
---
Loading libraries
```{r}
library(tidyverse)
```
1 MVP

Task 1.
Load in the country_data.csv file and take a look at it. What needs changed in this to make it tidy? Which columns need made into long format, and which need spread to rows?
```{r}
country_data <- read_csv("data/country_data.csv")

country_data
# the type column has to be split and moved to be columns, this means that we'll end up with one row for each country.
```

Task 2.
Do the appropriate pivoting of your columns using R
```{r}
country_data

long_data <- country_data %>%
  pivot_longer(cols = c(Y1999:Y2001), names_to = "year", values_to = "value")

long_data

country_alt_data <- pivot_wider(long_data,
  names_from = c("type", "year"),
  values_from = "value"
)

country_alt_data
```

Task 3.
Separate the country variable so you have the name in one column and the number in another.
```{r}
country_alt_data <- country_alt_data %>%
  separate(country, into = c("number", "country"), sep = " ")

country_alt_data
```

Task 4.
Unite the code_letter and code_numb variables so that they are both in one column, with no spaces separating them.
```{r}
country_alt_data_test <- country_alt_data %>%
  mutate(code_letter_numb = paste(code_letter, code_numb, sep = "")) %>%
  select(number, country, population_Y1999:code_letter_numb)

country_alt_data_test
```
